### 2019-07-11 2-Chapters/3-Chapter/chapter3.tex
Done for now
Done for end of conclusion

\abstractStartChapter{}%
%
\SMPyBandits{} is a library I have developed in the Python language since the beginning of my PhD.
It is designed to allow easy and fast numerical simulations on single-player and multi-players Multi-Armed Bandits (MAB) algorithms.
Its name stands for \emph{S}ingle- and \emph{M}ulti-\emph{P}layer \emph{Bandits} in P\emph{y}thon.
To the best of the authors' knowledge, it is the most exhaustive open-source implementation of state-of-the-art algorithms and different kinds of MAB models.
%
This chapter details the organization of the library and what it implements in terms of arm distributions, models, algorithms and visualizations.
Then we use it to perform a numerical comparison of the main state-of-the-art single-player bandit algorithms, and a study to compare time and memory costs of some of the most well-known and most widely used MAB algorithms.
%
Note that almost all the numerical simulations used in the rest of the thesis are based on SMPyBandits.

@@

We chose to present here the Python library \SMPyBandits{} in this chapter, rather than in the Appendix, because all the numerical experiments on single-player multi-armed bandits in Chapter~\ref{chapter:25}, and on more sophisticated models in the last two Chapters~\ref{chapter:5} and \ref{chapter:6} are built on \SMPyBandits.
%
We detailed three main points of our library:
$(i)$ its purpose and qualities,
$(ii)$ its organization,
and $(iii)$ an overview of its usage:
%

@@

\paragraph{Future works.}
%
% An interesting future work left on our library \SMPyBandits{} could be to implement variants of the single-player stochastic models, as well as variants for the multi-players or the non-stationary cases.
% For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits /SMPyBandits/issues/}}.
% For instance it would be interesting to extend the library for problems with non-finite arms, \eg, linear or contextual bandit (\href{https://github.com/SMPyBandits/SMPyBandits/issues/117}{ticket 117}),
% or to add support for the ``dynamic case'' of multi-players bandits to allow arrivals or departures of players (\href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{ticket 124}).
% %
% At the end of Chapter~\ref{chapter:5}, we present many extensions of the multi-players bandit model,
% and even if some have already been implemented, a major future work is to implement the most interesting ones
% (tickets \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{120}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{124}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/185}{185}).

@@

The most exciting thing that could happen to our \SMPyBandits{} library would be to see it gaining popularity!
Its documentation has seen already about $20000$ visits, \href{https://github.com/SMPyBandits/SMPyBandits/stargazers}{the project on GitHub had $90$ stars} in June $2019$, and based on the features requested and the emails received about it, we counted between $10$ to $20$ researchers in other labs who use or used \SMPyBandits.
While this is a good start, we believe that the library is mature and interesting enough to hope to see it being used by more people.
%
We have submitted a summary paper presenting \SMPyBandits{} \cite{SMPyBanditsJMLR} to the MLOSS track of the Journal of Machine Learning Research (JMLR), and we hope that it will be accepted, as it would give more visibility to this work.
%
As a personal note, I would like to continue working on \SMPyBandits, and implement the most interesting requested features, as well as maintain it, and possibly continue to add recent algorithms by following actively the research in this community.
I would also love to be able to teach a graduate or under-graduate course on reinforcement learning and multi-armed bandits in the next years, and use my library as a support to illustrate such course, as well as practical sessions.

>>>>

\abstractStartChapter{}%
%
\SMPyBandits{} is a library that has been developed in the Python language since the beginning of this PhD.
It is designed to allow easy and fast numerical simulations on single-player and multi-players Multi-Armed Bandits (MAB) algorithms.
Its name stands for \emph{S}ingle- and \emph{M}ulti-\emph{P}layer \emph{Bandits} in P\emph{y}thon.
To the best of the authors' knowledge, it is the most exhaustive open-source implementation of state-of-the-art algorithms and different kinds of MAB models.
%
This chapter details the organization of the library and what it implements in terms of arm distributions, models, algorithms and visualizations.
Then we use it to perform a numerical comparison of the main state-of-the-art single-player bandit algorithms, and a study to compare time and memory costs of some of the most well-known and most widely used MAB algorithms.
%
Note that almost all the numerical simulations used in the rest of the thesis are based on SMPyBandits.

@@

We chose to present here the Python library \SMPyBandits{} in this chapter, rather than in the Appendix, because all the numerical experiments on single-player multi-armed bandits in Chapter~\ref{chapter:25}, and on more sophisticated models in the last two Chapters~\ref{chapter:5} and \ref{chapter:6} are built on \SMPyBandits.
%
We detailed the three following main points of our library:
% $(i)$ its purpose and qualities,
% $(ii)$ its organization,
% and $(iii)$ an overview of its usage:
%

@@

\subsection*{Perspectives}
%
% An interesting future work left on our library \SMPyBandits{} could be to implement variants of the single-player stochastic models, as well as variants for the multi-players or the non-stationary cases.
% For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits /SMPyBandits/issues/}}.
% For instance it would be interesting to extend the library for problems with non-finite arms, \eg, linear or contextual bandit (\href{https://github.com/SMPyBandits/SMPyBandits/issues/117}{ticket 117}),
% or to add support for the ``dynamic case'' of multi-players bandits to allow arrivals or departures of players (\href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{ticket 124}).
% %
% At the end of Chapter~\ref{chapter:5}, we present many extensions of the multi-players bandit model,
% and even if some have already been implemented, a major future work is to implement the most interesting ones
% (tickets \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{120}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{124}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/185}{185}).

@@

An interesting task that I would have liked to complete is to interface the library with a web-based interactive demonstration, in order to allow anyone to launch simulations without any knowledge of programming.
It is already possible to reproduce some of the experiments presented in this thesis,
by following the instructions given in the documentation (see Section~\ref{sub:3:listResearchWorksUsingSMPyBandits}),
by using the Jupyter notebooks \cite{jupyter} made available%
\footnote{~These notebooks are hosted on both the GitHub repository of SMPyBandits and on my website on \href{https://perso.crans.org/besson/PhD/notebooks/}{\texttt{perso.crans.org/besson/PhD/notebooks/}}. They can be used locally if you install the library, but can also be used on cloud platforms, like Binder \href{https://mybinder.org/v2/gh/SMPyBandits/SMPyBandits/master}{\texttt{mybinder.org/v2/gh/SMPyBandits/SMPyBandits/master}} or Google Colab \href{https://colab.research.google.com/github/SMPyBandits/SMPyBandits/tree/master/notebooks/}{\texttt{colab.research.google.com/github/SMPyBandits/SMPyBandits/tree/master/notebooks/}}}.

Finally, the most exciting thing that could happen to our \SMPyBandits{} library would be to see it gaining popularity!
Its documentation has seen already about $20000$ visits, \href{https://github.com/SMPyBandits/SMPyBandits/stargazers}{the project on GitHub had $90$ stars} in June $2019$, and based on the features requested and the emails received about it, we counted between ten to twenty researchers in other labs who use or used \SMPyBandits.
While this is a good start, we believe that the library is mature and interesting enough to hope to see it being used by more people.
%
We have submitted a summary paper presenting \SMPyBandits{} \cite{SMPyBanditsJMLR} to the MLOSS track of the Journal of Machine Learning Research (JMLR), and we hope that it will be accepted, as it would give more visibility to this work.
%
As a personal note, I would like to continue working on \SMPyBandits, and implement the most interesting requested features, as well as maintain it, and possibly continue to add recent algorithms by following actively the research in this community.
I would also love to be able to teach an under-graduate course on reinforcement learning and bandits in the future, and to use my library as a support to illustrate a course and its practical sessions.

### 2019-07-11 2-Chapters/Conclusion/conclusion.tex
Done for end of conclusion

% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% \section{General Conclusion}
% \subsection*{General Conclusion}

@@

\paragraph{For SMPyBandits.}
%
A few tasks are left on our library SMPyBandits, a first one could be to implement new variants of the single-player stochastic models, as well as variants for the multi-players or the non-stationary cases.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits /SMPyBandits/issues/}}.
%
A second interesting task could be
% to extend the library for problems with non-finite arms, such as linear or contextual bandits (\href{https://github.com/SMPyBandits/SMPyBandits/issues/117}{ticket 117}),
to add support for the ``dynamic case'' of multi-players bandits to allow arrivals or departures of players (\href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{ticket 124}).
%
A third task that I would have liked to complete is to interface the library with a web-based interactive demonstration, in order to allow anyone to launch simulations without any knowledge of programming.
It is already possible to reproduce some of the experiments presented in this thesis,
by following the instructions given in the documentation (see Section~\ref{sub:3:listResearchWorksUsingSMPyBandits}),
by using the Jupyter notebooks \cite{jupyter} made available%
\footnote{~These notebooks are hosted on both the GitHub repository of SMPyBandits and on my website on \href{https://perso.crans.org/besson/PhD/notebooks/}{\texttt{perso.crans.org/besson/PhD/notebooks/}}. They can be used locally if you install the library, but can also be used on cloud platforms, like Binder \href{https://mybinder.org/v2/gh/SMPyBandits/SMPyBandits/master}{\texttt{mybinder.org/v2/gh/SMPyBandits/SMPyBandits/master}} or Google Colab \href{https://colab.research.google.com/github/SMPyBandits/SMPyBandits/tree/master/notebooks/}{\texttt{colab.research.google.com/github/SMPyBandits/SMPyBandits/tree/master/notebooks/}}}.

@@

% \hr{}

>>>>

% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% \section{General Conclusion}
\subsection*{Conclusion on our contributions}

@@

\paragraph{For our library SMPyBandits.}
%
A few tasks are left on SMPyBandits, a first one could be to implement new variants of the single-player stochastic models, as well as variants for the multi-players or the non-stationary cases.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits /SMPyBandits/issues/}}.
%
A second interesting task could be
% to extend the library for problems with non-finite arms, such as linear or contextual bandits (\href{https://github.com/SMPyBandits/SMPyBandits/issues/117}{ticket 117}),
to add support for the ``dynamic case'' of multi-players bandits to allow arrivals or departures of players (\href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{ticket 124}).

@@

\vfill{}
